Re-fit

### 2023-01-16 scripts/r/04_refit/refit_tr.Rmd
🐛 - include pseudopleuronectes_assasi

>>>>

# pseudopleuronectes_assasi

```{r pseudopleuronectes_assasi_setup}

# read csv
mpa <- read.delim("./data/analyses/tr/pseudopleuronectes_assasi/alldata.txt", header = T, sep = "") %>% 
  as_tibble()

atypical <- subset(mpa,Typicality=="atypical")
atypicalAF <- subset(atypical,Condition=="AF")
atypicalNF <- subset(atypical,Condition=="NF")
atypicalAF1 <- subset(atypicalAF,Vowel==1)
atypicalAF2 <- subset(atypicalAF,Vowel==2)
atypicalNF1 <- subset(atypicalNF,Vowel==1)
atypicalNF2 <- subset(atypicalNF,Vowel==2)
atypical1 <- subset(atypical,Vowel==1)
atypical2 <- subset(atypical,Vowel==2)
atypicalAFNF1 <- rbind(atypicalAF1,atypicalNF1)
NF <- subset(mpa,Condition=="NF")
NFa <- subset(NF,Typicality=="atypical")
NFm <- subset(NF,Typicality=="medium")
NFt <- subset(NF,Typicality=="typical")
NF1 <- subset(NF,Vowel==1)
NF2 <- subset(NF,Vowel==2)
```

```{r pseudopleuronectes_assasi_models}

NF1DurTyp <- lmer(Duration~Typicality+(1|Speaker)+(1|TargetColor),data=NF1,REML=FALSE)
NF1F0Typ <- lmer(MedianST~Sex+Typicality+(1|Speaker)+(1|TargetColor),data=NF1,REML=FALSE)
NF1IntTyp <- lmer(MedianInt~Typicality+(1|Speaker)+(1|TargetColor),data=NF1,REML=FALSE)
NF1DistTyp <- lmer(FormDist~Typicality+(1|Speaker)+(1|TargetColor),data=NF1,REML=FALSE)

```{r pseudopleuronectes_assasi_refitting}

# standardize
NF1 <- NF1 %>% 
    mutate(
    Duration_s = (Duration - mean(Duration, na.rm = TRUE)) / sd(Duration,  na.rm = TRUE),
    MedianST_s = (MedianST - mean(MedianST, na.rm = TRUE)) / sd(MedianST,  na.rm = TRUE),
    MedianInt_s = (MedianInt - mean(MedianInt, na.rm = TRUE)) / sd(MedianInt,  na.rm = TRUE),
    FormDist_s = (FormDist - mean(FormDist, na.rm = TRUE)) / sd(FormDist,  na.rm = TRUE),
    effect_cat = C(as.factor(Typicality), treatment),
    sex_s = as.factor(Sex),
    sex_s = C(sex_s, sum)
  )

pseudopleuronectes_assasi_1_dur_cat <- brm(
  Duration_s ~ 
         effect_cat + 
         (1|Speaker) + 
         (1|TargetColor),
  seed = 111,
  data = NF1, 
  cores = 4,  
  file = "./data/analyses/models/pseudopleuronectes_assasi_1_dur_cat"
  )

pseudopleuronectes_assasi_2_f0_cat <- brm(
  MedianST ~ 
         effect_cat + Sex +
         (1|Speaker) + 
         (1|TargetColor),
  seed = 111,
  data = NF1, 
  cores = 4,  
  file = "./data/analyses/models/pseudopleuronectes_assasi_2_f0_cat"
  )

pseudopleuronectes_assasi_3_int_cat <- brm(
  FormDist_s ~ 
         effect_cat + 
         (1|Speaker) + 
         (1|TargetColor),
  seed = 111,
  data = NF1, 
  cores = 4,  
  file = "./data/analyses/models/pseudopleuronectes_assasi_3_int_cat"
  )

pseudopleuronectes_assasi_4_formants_cat <- brm(
  MedianInt_s ~ 
         effect_cat + 
         (1|Speaker) + 
         (1|TargetColor),
  seed = 111,
  data = NF1, 
  cores = 4,  
  file = "./data/analyses/models/pseudopleuronectes_assasi_4_formants_cat"
  )
